---
title: R4DS_solutions
author: Lei Yan
date: '2018-12-23'
slug: r4ds-solutions
categories:
  - R
tags:
  - R4DS
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 5.6.7 Exercises
```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(nycflights13)
```
Creat `not_cancelled` for problems use.
```{r}
not_cancelled <- flights %>% filter(!is.na(dep_delay), !is.na(arr_delay))
```
### 1.
I don't like this question, so I choose to ignore it.

### 2.
Come up with another approach that will give you the same output as `not_cancelled %>% count(dest)` and `not_cancelled %>% count(tailnum, wt = distance)` (without using count()).
```{r}
not_cancelled %>%
  group_by(dest) %>%
  summarise(n = n())
```
```{r}
not_cancelled %>%
  group_by(tailnum) %>%
  summarise(n = sum(distance))
```

### 3.
Our definition of cancelled flights `(is.na(dep_delay) | is.na(arr_delay) )` is slightly suboptimal. Why? Which is the most important column?

Because there is no such flights which are cancelled at departure time but have non-`NA` arrival time. 
We can verify this using the code below.
```{r}
flights %>%
  filter(is.na(dep_delay), !is.na(arr_delay))
```
So, `dep_delay` is the most important column.

### 4.
Look at the number of cancelled flights per day. Is there a pattern? Is the proportion of cancelled flights related to the average delay?

```{r}
flights %>%
  group_by(year, month, day) %>%
  summarise(cancelled = sum(is.na(dep_delay)),
            proportion = mean(is.na(dep_delay)),
            aver_dep = mean(dep_delay, na.rm = T),
            aver_arr = mean(arr_delay, na.rm = T)
            ) %>%
  ggplot(mapping = aes(x = proportion)) +
  geom_point(mapping = aes(y = aver_dep), color = 'blue', alpha = 0.5) +
  geom_point(mapping = aes(y = aver_arr), color = 'red', alpha = 0.5) + 
  ylab('average delay(min)')
```

### 5.
Which carrier has the worst delays? Challenge: can you disentangle the effects of bad airports vs. bad carriers? Why/why not? (Hint: think about `flights %>% group_by(carrier, dest) %>% summarise(n())`)

Let's find out the carrier which has the worst delays.
```{r message=FALSE}
flights %>%
  group_by(carrier) %>%
  summarise(max_dep = max(dep_delay, na.rm = T),
            max_arr = max(arr_delay, na.rm = T)) %>%
  arrange(desc(max_dep, max_arr)) %>% 
  top_n(1)
  
```

Use the hint:
```{r}
flights %>% 
  group_by(carrier, dest) %>%
  summarise(n())
```

### 6.
What does the `sort` argument to `count()` do. When might you use it?

`sort` if `TRUE` will sort output in descending order of `n`